Discrete Quantum Theories and Computing

### 2018-04-02 dissertation.tex
dissertation.lyx acknowledgments Updates...

\begin{acknowledgments}Thank Prof. Andrew Hanson, Prof. Gerardo Ortiz,
and Prof. Amr Sabry for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
with me. They becomes the main part of my thesis, especially most
of Chapter~\ref{chap:DQT=000026DQC} is based on ``Geometry of discrete
quantum computing''~\cite{geometry2013} and ``Discrete quantum
theories''~\cite{DQT2014}; most of Chapter~\ref{chap:DQT=000026DQC}
is based on ``Quantum Interval-Valued Probability: Contextuality
and the Born Rule'' \cite{THOS2017}. Together with Prof. Dylan Thurston
and Prof. Shouhong Wang, thank you for getting together to understand
what I did and passing my dissertation proposal Spring 2017. Also,
thank Prof. Dylan Thurston for serving in my advisory committee and
my Tier 3 committee, with other advisory committee members passing
my Computer Science qualifying exam Spring 2016. Especially, my survey
of real computation in the qualifying exam inspires me the comparison
of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
Thank Prof. Lawrence Moss for inviting me to presented my results
in the interdisciplinary logic seminar and SICE theory seminar, co-chairing
my Tier 3 committee, writing an assessment letter for me, and drawing
my attention on Prof. Abramsky's paper~\cite{Abramsky2012}, which
inspired me to merge quantum probability with discrete quantum theories.
Thanks John Gardiner for inspiring discussion on the difficulties
merging quantum probability with discrete quantum theories~\cite{Gardiner2014}.
An improved work consists of Sec.~\ref{sec:Toward-IVPM} \end{acknowledgments}
\begin{abstract}
Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems.
\end{abstract}
\tableofcontents{}

>>>>

\begin{acknowledgments}Thank Prof. Gerardo Ortiz, Prof. Amr Sabry,
and Prof. Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
with me, and enormous other things. These papers become the main part
of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
is based on ``Geometry of discrete quantum computing''~\cite{geometry2013}
and ``Discrete quantum theories'' (DQT)~\cite{DQT2014}; most of
Chapter~\ref{chap:DQT=000026DQC} is based on ``Quantum Interval-Valued
Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2017}.
Together with Prof. Dylan Thurston and Prof. Shouhong Wang, thank
you for getting together to understand what I did and passing my dissertation
proposal Spring 2017. Also, thank Prof. Dylan Thurston for serving
in my advisory committee and my Tier 3 committee, with other advisory
committee members passing my Computer Science qualifying exam Spring
2016. Especially, my survey of real computation in the qualifying
exam inspires me the comparison of quantum computer and analog computer
in Chapter~\ref{chap:Introduction}. Thank Prof. Lawrence Moss for
inviting me to present our results in the interdisciplinary logic
seminar and SICE theory seminar, co-chairing my Tier 3 committee,
writing an assessment letter for me, and drawing my attention on Prof.
Abramsky's paper~\cite{Abramsky2012}, which inspired me to merge
quantum probability with discrete quantum theories. Thank John Gardiner
for inspiring discussion on the difficulties merging them~\cite{Gardiner2014}.
These results are improved and motivated the transition from DQT to
QIVPM in Sec.~\ref{sec:Toward-IVPM}. Thank Prof. Tom Lewis for helping
me organize the unpublished deterministic quantum algorithms in the
term paper for SLST-T501 Academic Writing course. Thank Instructor
Traci Nagle\end{acknowledgments}
\begin{abstract}
Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems.
\end{abstract}
\tableofcontents{}
